Comparing Early Evolution of Flames in X-ray Bursts in Two and Three Dimensions

### 2023-03-14 xrb3/paper.tex
fix caption

\begin{figure*}[t]
\centering
%\epsscale{0.75}
\plotone{flame_wave_1000Hz_25cm_smallplt174562_slice}
%\epsscale{1.0}
\caption{\label{fig:3dslice} A vertical slice through the three-dimensional
simulation {\color{red} at 40~ms} showing the entire domain from the side.  The
flame structure is clearly seen. }
\end{figure*}

>>>>

\begin{figure*}[t]
\centering
%\epsscale{0.75}
\plotone{flame_wave_1000Hz_25cm_smallplt174562_slice}
%\epsscale{1.0}
\caption{\label{fig:3dslice} A vertical slice through the three-dimensional
simulation at 40~ms showing a region centered on the flame viewed from the side.  The
flame structure is clearly seen. }
\end{figure*}
